Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-21 paper/paper.tex
Debracket
Support

There are two main approaches for solving MCS. The first approach (described in \cref{CP}) is based
on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
maximum clique problem. Both approaches are described for undirected, unlabelled graphs; their
extension to richer graphs is discussed in \cref{extension}.  (Other approaches have been tried,
mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
\cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
\cite{UpcomingIJCAIPaper}.)

@@

Labels and directed edges usually simplify the solution process, both for CP and clique-based
approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in
association graphs; edge labels tighten edge constraints for CP, and make the association graph
sparser for clique-based approaches. It is worth noting that edge constraints do not help CP
approaches to do more filtering so long as $\bot$ remains in variable domains: every pair of
variables $(x_i, x_j)$ having  $D(x_i) \neq \emptyset$ and $\bot \in D(x_j)$ is arc consistent,
since $\bot$ is a support for any value $u \in D(x_i)$. However, as soon as $\bot$ is removed from
domains (i.e.\ when the number of variables assigned to $\bot$ has reached the best known bound on
the size of the MCS), maintaining arc consistency may filter values, and then the tighter constraints
increase the opportunities for filtering.

>>>>

There are two main approaches for solving MCS. The first approach (described in \cref{CP}) is based
on CP, whilst the second (described in \cref{clique}) is based on a reformulation of MCS into a
maximum clique problem. Both approaches are described for undirected, unlabelled graphs; their
extension to richer graphs is discussed in \cref{extension}.  Other approaches have been tried,
mixed integer programming \cite{DBLP:journals/anor/PivaS12} and heuristics
\cite{DBLP:journals/jcisd/EnglertK15}; SAT encodings seem to struggle even for subgraph isomorphism
\cite{UpcomingIJCAIPaper}.

@@

Labels and directed edges usually simplify the solution process, both for CP and clique-based
approaches: vertex labels reduce domain sizes for CP, and the number of matching nodes in
association graphs; edge labels tighten edge constraints for CP, and make the association graph
sparser for clique-based approaches. It is worth noting that edge constraints do not help CP
approaches to do more filtering so long as $\bot$ remains in variable domains: every pair of
variables $(x_i, x_j)$ having  $\bot \in D(x_j)$ is arc consistent,
since $\bot$ is a support for any value $u \in D(x_i)$. However, as soon as $\bot$ is removed from
domains (i.e.\ when the number of variables assigned to $\bot$ has reached the best known bound on
the size of the MCS), maintaining arc consistency may filter values, and then tighter constraints
increase the opportunities for filtering.
